Meta RL analyses

### 2019-02-26 meta_RL_analyses.Rmd
Better plots, and getting rid of some redundancies

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout")

name_run_type = function(run_type) { # names for plotting
  case_when(run_type == "basic" ~ "Targeted 10% holdout",
            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
            T ~ run_type)
}

@@

```{r}
summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +
    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
    geom_point(stat="summary", fun.y=mean, size=2) +
    geom_errorbar(stat="summary", 
                  fun.ymin=function(x) {mean(x) - 1.96*sd(x)/sqrt(length(x))},
                  fun.ymax=function(x) {mean(x) + 1.96*sd(x)/sqrt(length(x))},
                  width=0.25) +
    scale_color_brewer(palette=palette)

@@

summary_plot(reward_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type)
```

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type) + 
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

@@

```{r}
language_d = load_d(results_dir, c("language", "language_noncompositional", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"), num_runs, "new_language_rewards")

@@

```{r}
avg_language_d = language_d %>%
  select(-game_str) %>%
  filter(epoch == 0) %>%
  group_by(run_type, game_type, is_new_game) %>%
  summarize(avg_reward = mean(reward), sd_reward=sd(reward),
            se_reward = sd_reward/sqrt(n()), 
            ci_lo = avg_reward - 1.96*se_reward, 
            ci_hi = avg_reward + 1.96*se_reward)
```

```{r}
ggplot(language_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=run_type, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  scale_color_brewer(palette="Set2") 
```

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
                               ), num_runs, "new_language_meta_true_losses")

@@

```{r}
avg_lang_meta_d = lang_meta_d %>%
  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(run_type, named_run_type, meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

```{r}
ggplot(avg_lang_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(. ~ named_run_type)
```

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
```
# embeddings

>>>>

result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   #"language", "language_simplified",
                   "language_noncompositional_old", "language_simplified_random_holdout")

name_run_type = function(run_type) { # names for plotting
  case_when(run_type == "basic" ~ "Targeted 10% holdout",
            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
            run_type == "language_noncompositional_old" ~ "Old language (targeted 10%)",
            run_type == "language_simplified" ~ "Old language (targeted 10%)",
            run_type == "language_simplified_random_holdout" ~ "Language (random 50%)",
            T ~ run_type)
}

@@

```{r}
name_var = function(var) { # var names for plotting
  case_when(var %in% c("is_new", "is_new_game") ~ "Held out?",
            var == "game_type" ~ "Game",
            var %in% c("run_type", "named_run_type") ~ "Run type",
#            var == "reward" ~ "Reward",
            grepl("reward", var) ~ "Average Reward",
            T ~ var)
  }

summary_plot = function(data,  x_var, y_var, color_var, baseline_data=NULL, palette="Set2") {
  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +
    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
    geom_point(stat="summary", fun.y=mean, size=2) +
    geom_errorbar(stat="summary", 
                  fun.ymin=function(x) {mean(x) - 1.96*sd(x)/sqrt(length(x))},
                  fun.ymax=function(x) {mean(x) + 1.96*sd(x)/sqrt(length(x))},
                  width=0.25) +
    scale_color_brewer(palette=palette) +
    labs(x=name_var(x_var), y=name_var(y_var)) +
    guides(color=guide_legend(title=NULL))

@@

# summary_plot(reward_d %>%
#                filter(epoch == 0),
#              "game_type", "reward", "is_new_game",
#              simple_baselines) +
#   facet_wrap(. ~ named_run_type)
```

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type %in% c("basic", "basic_random_holdout_longer")),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

@@

```{r}
language_d = load_d(results_dir, c("language_noncompositional_old", 
                                   #"language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")

@@

```{r}
ggplot(language_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=named_run_type, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  geom_point(aes(group=as.factor(run)),
             size=3,
             stat="summary", fun.y="mean",
             position=position_dodge(width=0.9)) +
  scale_color_brewer(palette="Set2") + 
  ylim(-0.6, 0.6) +
  labs(x="Run type",
       y="Reward density") + 
  guides(fill=guide_legend(title="Run"))
ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
```

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             simple_baselines) +
  facet_wrap(. ~ run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("writing/figures/language_basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout"
                               ), num_runs, "new_language_meta_true_losses")

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
```
# embeddings
